Categorical Predictor Embeddings in Actuarial Modeling

### 2021-02-03 manuscript/manuscript.Rmd
more stuff

@@

To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the 
root mean square error (RMSE) on the predicted and actual paid amounts.

@@

>>>>

(maybe include a second nn with actual hidden layers?)

@@

To evaluate these baseline models and other models in this paper, we perform 10-fold 
cross validation and compare the 
root mean square error (RMSE) on the predicted and actual paid amounts.
(somehwere we should say we're not doing a kaggle competition here and the performance metrics are really meant
to show that the models aren't complete shit)
(maybe a couple boxplots showing metrics for baseline models)

@@

Description of tabnet, talk about how it's related to embeddings, show some plots 
like \@ref(fig:masks) etc.

```{r masks, echo = FALSE, fig.cap = "blahblah", out.width = "100%", fig.align = "center"}
knitr::include_graphics("images/masks.png")
```
